Observation of the Torsional Motion of a Solar Jet at the Limb

### 2016-08-18 paper/ms_temp_paper.tex
fixing further figures

\begin{pycode}[T-D-plots]
import pickle
import def_spic
import def_spic_SST

path_131 = manager.data_file('jet_picks/131_records.pik')
path_171 = manager.data_file('jet_picks/171_records.pik')
path_211 = manager.data_file('jet_picks/211_records.pik')
path_304 = manager.data_file('jet_picks/304_records.pik')
path_335 = manager.data_file('jet_picks/335_records.pik')
ha_path = manager.data_file('jet_picks/H_alpha_records.pik')

@@

fig = plt.figure()
plt.plot(e_times_131, lengths_131, color='green', label='13.1 nm')
plt.plot(e_times_171, lengths_171, color='yellow', label='17.1 nm')
plt.plot(e_times_211, lengths_211, color='purple', label='21.1 nm')
plt.plot(e_times_304, lengths_304, color='orange', label='30.4 nm')
plt.plot(e_times_335, lengths_335, color='blue', label='33.5 nm')
plt.plot(e_times_Ha, lengths_Ha, color='darkgoldenrod', label='656.28 nm')
plt.xlabel('Time [UCT]')
plt.ylabel('Length [Mm]')
plt.title('Length of the Jet over time')
fig.autofmt_xdate()
td_fig = manager.save_figure('t-d-plot', fig)
td_fig.subfig_width = r"\columnwidth"
td_fig.caption = ""
#td_fig.caption = r"Darkgold = H$\alpha$, Blue = 33.5 nm, Orange = 30.4 nm, Purple = 21.1 nm, Yellow = 17.1 nm, Green = 13.1 nm. The CRISP observations end earlier than thewhole evolution of the jet, and the top of the jet is cut off by the top og the image. Therefore we ignore the flatline at the top of the H$\alpha$ line starting at $07:42$"
\end{pycode}

@@

dop_frames = [76,77,78,79,80,81,82,83,85]
frame_numbers = np.arange(75,90)

@@

# new figure using subplot2grid specificially
fig = plt.figure(figsize=texfigure.figsize(pytex, height_ratio=1.3, figure_width_context='textwidth'))
gs = gridspec.GridSpec(3,8)
ax1 = plt.subplot(gs[0,0:2])
ax2 = plt.subplot(gs[0,2:4])
ax3 = plt.subplot(gs[0,4:6])
ax4 = plt.subplot(gs[0,6:8])
ax5 = plt.subplot(gs[1,0:2])
ax6 = plt.subplot(gs[1,2:4])
ax7 = plt.subplot(gs[1,4:6])
ax8 = plt.subplot(gs[1,6:8])
ax9 = plt.subplot(gs[2,0:2])
ax10 = plt.subplot(gs[2,3:])

ax_list = [ax1, ax2, ax3, ax4, ax5,
           ax6, ax7, ax8, ax9]

@@

line_segments.set_array(np.arange(1,len(slit_list)+1))
ax10.add_collection(line_segments)
ax10.axis([1,xy_slit[0].shape[0]-1,-1.6,1.6])
ax10.axhline(0, color='k', linewidth=0.5)

axcb = fig.colorbar(line_segments)
axcb.set_label('Frame Number')
axcb.set_ticks(range(1, len(xy_slit)+1))
#ax10.set_title('Slit across')
ax10.set_xlabel('Distance Along Slit [pixels]')
ax10.set_ylabel('Velocity {}'.format(dop_fin.unit._repr_latex_()))
plt.sci(line_segments)

@@

fig, ax = plt.subplots(figsize=texfigure.figsize(pytex, reference='temp-slit'))
temp_slit = texfigure.Figure(fig, reference='temp_slit')
temp_slit.caption = "The AIA maps were processed into temperature maps, and a slit was taken at the half height, perpendicular to the axis of evolution. The temperature maps were taken for the time over which the second acceleration of material occured. The colorbar indicates the passage of time and the various lines applicable to the slits is demonstrated."
temp_slit = manager.save_figure('temp_slit')

>>>>

\begin{pycode}[T-D-plots]
import pickle
import def_spic
import def_spic_SST
from matplotlib.dates import DateFormatter

path_131 = manager.data_file('131_records.pik')
path_171 = manager.data_file('171_records.pik')
path_211 = manager.data_file('211_records.pik')
path_304 = manager.data_file('304_records.pik')
path_335 = manager.data_file('335_records.pik')
ha_path = manager.data_file('H_alpha_records.pik')

@@

fig = plt.figure()
plt.plot(e_times_131, lengths_131, color='green', label='13.1 nm')
plt.plot(e_times_171, lengths_171, color='yellow', label='17.1 nm')
plt.plot(e_times_211, lengths_211, color='purple', label='21.1 nm')
plt.plot(e_times_304, lengths_304, color='orange', label='30.4 nm')
plt.plot(e_times_335, lengths_335, color='blue', label='33.5 nm')
plt.plot(e_times_Ha, lengths_Ha, color='darkgoldenrod', label='656.28 nm')
plt.xlabel('Time [UCT]')
plt.ylabel('Length [Mm]')
plt.title('Length of the Jet over time')
fig.autofmt_xdate()

formatter = DateFormatter('%H:%M:%S')
plt.gcf().axes[0].xaxis.set_major_formatter(formatter)

td_fig = manager.save_figure('t-d-plot', fig)
td_fig.subfig_width = r"\columnwidth"
td_fig.caption = ""
#td_fig.caption = r"Darkgold = H$\alpha$, Blue = 33.5 nm, Orange = 30.4 nm, Purple = 21.1 nm, Yellow = 17.1 nm, Green = 13.1 nm. The CRISP observations end earlier than thewhole evolution of the jet, and the top of the jet is cut off by the top og the image. Therefore we ignore the flatline at the top of the H$\alpha$ line starting at $07:42$"
\end{pycode}

@@

#dop_frames = [76,77,78,79,80,81,82,83,85]
dop_frames = [76,77,78,79,80,81,82,83,85,86,87,88,89]
frame_numbers = np.arange(75,90)

@@

# new figure using subplot2grid specificially
fig = plt.figure(figsize=texfigure.figsize(pytex, height_ratio=1.3, figure_width_context='textwidth'))
gs = gridspec.GridSpec(3,8)
ax1 = plt.subplot(gs[0,0:2])
ax2 = plt.subplot(gs[0,2:4])
ax3 = plt.subplot(gs[0,4:6])
ax4 = plt.subplot(gs[0,6:8])
ax5 = plt.subplot(gs[1,0:2])
ax6 = plt.subplot(gs[1,2:4])
ax7 = plt.subplot(gs[1,4:6])
ax8 = plt.subplot(gs[1,6:8])
ax9 = plt.subplot(gs[2,0:2])
ax10 = plt.subplot(gs[2,2:4])
ax11 = plt.subplot(gs[2,4:6])
ax12 = plt.subplot(gs[2,6:8])

ax_list = [ax1, ax2, ax3, ax4, ax5, ax6,
           ax7, ax8, ax9, ax10, ax11, ax12]

@@

line_segments.set_array(np.arange(1,len(slit_list)+1))
#ax10.add_collection(line_segments)
#ax10.axis([1,xy_slit[0].shape[0]-1,-1.6,1.6])
#ax10.axhline(0, color='k', linewidth=0.5)

#axcb = fig.colorbar(line_segments)
#axcb.set_label('Frame Number')
#axcb.set_ticks(range(1, len(xy_slit)+1))
#ax10.set_title('Slit across')
#ax10.set_xlabel('Distance Along Slit [pixels]')
#ax10.set_ylabel('Velocity {}'.format(dop_fin.unit._repr_latex_()))
#plt.sci(line_segments)

@@

fig, ax = plt.subplots(figsize=texfigure.figsize(pytex))
temp_slit = manager.save_figure('temp-slit', fig)
temp_slit.caption = "The AIA maps were processed into temperature maps, and a slit was taken at the half height, perpendicular to the axis of evolution. The temperature maps were taken for the time over which the second acceleration of material occured. The colorbar indicates the passage of time and the various lines applicable to the slits is demonstrated."
